---
title: "Atlas Aquatica"
format: 
  gfm:
    code-fold: true
---

Our endeavor, the Atlas Aquatica, is a result of an international collaboration among the Centro para la Biodiversidad Marina y la Conservación in Mexico; the Scripps Institution of Oceanography -- University of California San Diego, and the University of California Santa Barbara, USA; the University of British Columbia and the Simon Fraser University, Canada; and the TREES, North-West University, Potchefstroom, South Africa. Here, we will detail the distribution of the diving sites, provide a global economic estimate of the diving operators, and identify gaps in knowledge.

## Datasets 

We have built three main datasets using webscraping and surveyed data.

1.  A dataset of diving areas webscraped from Flickr images:

```{r, echo=TRUE, warning=FALSE, message=FALSE}
library(tidyverse)
read_rds("data/diving_sites_flickr_webscraped_images.RDS") |> 
          glimpse()
```

2. A dataset of coastal infrastructures (hotels, airports, marinas and ports): 

```{r, echo=TRUE, warning=FALSE, message=FALSE}
read_rds("data/coastal_infraestructure_v1.RDS") |> 
          glimpse()
```

3. A dataset of the scuba diving operators webscraped with their survey responses:

```{r, echo=TRUE, warning=FALSE, message=FALSE}
read_csv("data/scuba_diving_operators_v_1_11102022_encr.csv") |> 
          glimpse()
```


The diving operators dataset has been encrypted and some information omitted in order to protect the privacy of the operators. 



4. Literature review of marine tourism economic estimates:

```{r, echo=TRUE, warning=FALSE, message=FALSE}
read_csv("data/Literature_economic_value.csv") |> 
          glimpse()
```
